Supp mat: time series paper

### 2017-07-07 writing/supp_mat_draft.tex
changed code to allow relative directories

We see that the distribution of \(T_{min}\) is almost identical to that
in the main manuscript. This is perhaps not surprising as most time
series that would signficantly increase or decrease linearly would
probably also significantly increase or decrease at an exponential rate.
Further, the calculations here and in the main manuscript both use
linear regression, and both estimate the same number of parameters.

>>>>

We see that the distribution of \(T_{min}\) is almost identical to that
in the main manuscript. This is perhaps not surprising as most time
series that would significantly increase or decrease linearly would
probably also significantly increase or decrease at an exponential rate.
Further, the calculations here and in the main manuscript both use
linear regression, and both estimate the same number of parameters.
